\title{CSE311 Project Proposal}
\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}


\begin{document}
\include{coverpage}


\section*{Introduction}

School management is an important task for the administrators. But for school containing more than 50 students it’s quite impossible to store the information of the teachers and students efficiently through stacks of papers. It is also impossible to make small changes, ensure security of the information or to get easy access of the information. That’s why in our web application an administrator can easily save the information of teacher, student. Here in the website the administrator can update, save information, keep track of everything and maintain the security of the information easily. 


\section*{Objective}

\begin{itemize}
  \item The information of the students, teachers can be managed easily by the administration efficiently.
  \item The students and their guardians can see the student’s grades, class routine, attendance report, school notices.
  \item The teachers can easily give grades, attendance to the students, see their progress.
  \item The students can also contact their teachers if they need help.
\end{itemize}

\section*{Target Customers}

\begin{enumerate}
  \item \textbf{School:} 
  \begin{itemize}
    \item Administrators: the admins can easily keep the information of the teachers, students.
    \item Students: the students can see their grades, information, routine, attendance.
    \item Teachers: the teachers can give students grades, get routine etc.

  \end{itemize}
  \item \textbf{University:} the website can be used in university level with some changes.
\end{enumerate}
\section*{Value Proposition}

The website will help to increase efficiency and reduce the dependency on papers by easily saving the information in the database. The school can also give their notices on the website, manage the student, teacher information easily which is why security of the information will increase, updating them will become a matter of minutes. 

\section*{Web Application Feature and description}

The web page will open with a general view and anyone accessing the domain will be able to view it.  Here all the school notices, admission notices, achievements of school will be seen. At the top left/right corner of a vertical tab there will be a log in button. From where a student or a teacher with their ID and password to log in to their profile. Initially an account is created by the admins and they also set their ID, password, the password can be later changed by the user.
\setlength{\parskip}{1em}


\textbf{A student can:}
\begin{itemize}
  \item See their attendance
  \item Class and school wise notices
  \item Class notice and routine
  \item Their grade
  \item Can get the email of the teacher
\end{itemize}
\setlength{\parskip}{1em}


\textbf{A teacher can:}
\begin{itemize}
  \item Take attendance of their assigned class
  \item See their class routine and also of class wise(like routine of class 1/2 )
  \item Grade the students
  \item Get the contact information of the students
  \item Can see and also give(of their assigned class) the notices
\end{itemize}
\section*{Tools and Resources}
\begin{itemize}
  \item HTML
  \item JavaScript
  \item MySQL
  \item PHP
  \item CSS
  \item Web server
\end{itemize}
\section*{Challenges}
The administrators need to make sure to give the appropriate permission to fixed type of users. The cost is also an important factor as there may be image files of the users and need a lot of memory for saving so many information of the users. UI need to be simple and easy so that normal people can also use it easily.

\end{document}

